---
title: "3 pass depletion population and power estimate"
author: "Ben Williams and Sara Miller"
date: "Dec 13, 2016"
output: pdf_document
---

**All stream habitats combined**

```{r combine, echo=F, warning=F, message=F, error=F}
source('../code/threep.R')
dat <- read.csv('../data/capture_dat_2016.csv')
combined <- threep(dat)
source('../code/threep_Sim.R')
combined2 <- threep_sim(combined$C,combined$k) 
source('../code/Sim.R')
N1<-136 #last year's MLE <-------------------------------------------ADJUST THIS EACH YEAR!!!!!!!!!!!!!!!!!!
nsims<-10000 #number of simulations (btw 1,000 and 10,000)
combined3<-Sim(N1,combined$N2, combined$p, nsims, combined$k)
```

The population estimate is `r combined$N` with a variance of `r combined$N.var` and standard error of `r combined$N.se`.  
With a projected MLE of $\hat{N} =$ `r combined$N*4` and lower and upper 95% CI of `r combined$mleLL` and `r combined$mleUL`, respectively.

Chi-squared test is not significant with $X^2=$ `r combined$x2` with a $X^2_{crit}$ value of `r combined$x2.crit` and p-value of `r combined$x2.p`.

A population estimate based upon the regression method is `r combined$Popest`.

```{r comb_fig, echo=F}
combined$gplot
```

A Student's t-test with 2 degress of freedom was used to test the null hypothesis that both estimates (last year's abundance and this year's abundance) came from populations of equal size, with one degree of freedom associated with each estimate. Significance was evaluated at ${\alpha}$ =0.05, 0.10, and 0.20 levels. For the pair of population abundances, 10,000 simulations of the 3 pass sampling were conducted and power was estimated as the proportion of simulations where the null hypothesis was rejected. During each simulation, the probability of capture was the same for both populations sampled (based on the current year's value) and held constant for all three sampling events, per model assumptions. 

For N1=`r N1` and N2=`r combined$N*4` and using a probability of capture of `r combined3$p`,   

- the power for p-value $\leq$ 0.05 significance level is `r combined3$pow95_percent`%,
&nbsp;
- the power for p-value $\leq$ 0.10 significance level is  `r combined3$pow90_percent`%, and 
&nbsp;
- the power for p-value $\leq$ 0.20 significance level is `r combined3$pow80_percent`%.

**Only pool habitats**
```{r pool, echo=F, warning=F, message=F, error=F, as.is=T}
pool <- threep(subset(dat, habitat=="P"))
```

The population estimate is `r pool$N` with a variance of `r pool$N.var` and standard error of `r pool$N.se`.  
With a projected MLE of $\hat{N} =$ `r pool$N*4` and lower and upper 95% CI of `r pool$mleLL` and `r pool$mleUL`, respectively.

Chi-squared test is not significant with $X^2=$ `r pool$x2` with a $X^2_{crit}$ value of `r pool$x2.crit` and p-value of `r pool$x2.p`.


A population estimate based upon the regression method is `r pool$Popest`.

```{r pool_fig, echo=F, eval=T}
pool$gplot
```

